% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\topmargin=-0.6in  % start text higher on the page
\setlength{\textheight}{11in} % increase text height to fit resume on 1 page
\usepackage{color}

\begin{document}  
\name{COLTON KOHNKE}
\address{1221 Illinois Street Apt. 2E \\ Golden, CO 80401 \\ (360) 813-2795 \\ ckohnke@mines.edu }

\begin{resume}                        

\section{EDUCATION} \textbf{Colorado School of Mines, Golden, CO} \hfill B.S. May 2014 \\
                Geophysics \& Geophysical Engineering \hfill CUM GPA 3.46 \\
                \textcolor{white}{...} \hfill Major GPA 3.61 \\
                \textbf{Professional Organizations}
                \begin{itemize}
                 \item Society of Exploration Geophysicists Student Member (SEG)
                 \item European Association of Geoscientists and Engineers (EAGE)
                \end{itemize}

\section{WORK \\ EXPERIENCE}
		  %\begin{tabular}{p{3in} r} 
			\textbf{Chevron of North America, Bakersfield, CA} \hfill Summer 2013 \\
			Upstream Technical Computer G{\&}G Support Intern
		  		\begin{itemize}
		  		\item Designed, developed, documented and deployed a new error reporting system to ensure well data integrity between 						multiple databases.
		  		\item Assessed opportunity of a new database/software system for seismic metadata to increase efficiency and safety while decreasing cost.
		  		\item Worked with Data Analyst and Asset Development teams to standardize well status symbols for use within the San Jaoquin Valley.
		  		\end{itemize}
		  		
			\textbf{Ventyx, Greenwood Village, CO} \hfill Summer 2012 - June 2013 \\
			MineScape Engineer Intern
                  %\end{tabular}	
                   \begin{itemize} % \item[] prevents a bullet from appearing
                    \item Wrote, debugged, tested and integrated code into MineScape software.
                    \item Tested the new MineScape 5.4 release.
                    \item Traveled and assisted clients with overburden stratigraphic modeling and \\geophysical interpretation on an 							open-pit coal mine.
                    \item Wrote and updated documentation for consumer utilization.
				   \end{itemize} 

\section{ENGINEERING \\ \& TECHNICAL \\ SKILLS} 
		\begin{itemize}
		\item MineScape, MineScape Programming Language, Geolog, OpenWorks, Petrel.
		\item JAVA/C++, MatLab, Python, R, LaTeX, and Mathematica.
		\item Geological Lab Experience, Geophysical Field Methods, Geophysical Survey \\ Design, GPS, Field and Office Safety, Well-Log Analysis.
		\item AutoCAD, SolidWorks; Microsoft Excel, Word, Powerpoint, Publisher.
		\item Linux/UNIX, Windows, and Mac OS.
		%\item Finite Element Analysis, Systems, Computer Aided Data Acquisition, Graphical and Written Design Proposals, Oral Presentation, Technical Writing, Formal Proposal Writing, Budgeting, and Scheduling.
		\end{itemize}
		
\section{PROJECT \\ EXPERIENCE}
		  %\begin{itemize}
			 %\item
            \textbf{Senior Design: Exploratory Analysis of Field Seismic Data} - Senior capstone project written in JAVA to quickly and accurately analyze seismic data in a field setting. Features include an interactive display of survey geometry, seismograms and simple processing tools. Expanding features to include field data from other methods (gravity, magnetics, DC/SP, GPR, and EM) as time permits.
			 
			\textbf{Geophysics Field Camp 2013} - Project to characterize the geothermal potential of Pagosa Springs, CO. Involved two weeks in the field gathering Gravity, Magnetics, EM, GPR, DC/SP, and Seismic data. This was followed by two weeks of data processing and technical report writing. Conclusions were published by the Colorado School of Mines Department of Geophysics.
			 
		   %\textbf{EPICS II: Geophysics Design} - Projects involving use of data analysis tools, such as R and JAVA, to interpret 					various data sets to solve a problem. Projects included analysis of sunspot data, correlation of local snowfall data, 					well-log analysis and finding \\ major driving forces for change in Lake Powell's water depth.
		   
		   %\textbf{EPICS I: Playground for the Disabled in South Africa} - Project \\involving research, conceptual design, graphical 				representation, subsystem analysis, materials list and budget of a playground for disabled children. Finalist in the 				EPICS 			competition.
		  %\end{itemize}

\section{OTHER \\ EXPERIENCE}
		  \begin{itemize}
		    \item Advanced Engineering Math Grader - Fall 2013.
		    \item Expected JAVA course Teaching Assistant - Spring 2014.
			\item High Grade Literary Journal Poetry Editor.			
			%\item Colorado School of Mines Varsity Swim Team.
			%\item Co-Founder and Officer of Mines Urban Gaming Club.
			\item Colorado School of Mines Peer Mentor.
			%\item Employment with the YMCA \& CSM Student Recreation Center.
		  \end{itemize}

\section{HONORS} 
	\begin{itemize}
	 \item Newmont Mining Scholar.
	 \item Naval Dolphin Scholarship Foundation Recipient.
	\end{itemize}
	 
%\section{{EXTRA-CURRICULAR \\ ACTIVITIES}} 
%	\begin{itemize}
%	 \item 
%	\end{itemize}
	 
\end{resume} 
\end{document}









